SubsidyExplorer - Step 6: Run Model

### 2020-09-16 scripts/07_proposals.Rmd
running proposal results again

# Directories for the output files generated by this script
results_dir <- here::here("results", "07-proposals/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

@@

subsidy_types_sorted_sumaila <- c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types)
```

@@

```{r}
# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.66
```

@@

   # Get all Cap/Tier conditions
   cap_tier = 
     list("on_off" = selected_proposal$cap_on_off,
          "subsidy_types" = unlist(str_split(selected_proposal$cap_subsidy_types, ", ")),
          "tier_number" = selected_proposal$cap_tier_number,
          "tier_system" = selected_proposal$tier_system,
          "two_tier_cutoff" = selected_proposal$two_tier_cutoff,
          "three_tier_cutoff" = as.numeric(unlist(str_split(
          selected_proposal$three_tier_cutoff, ", "
          ))),
          "tier1_cap_rule" = selected_proposal$tier1_cap_rule,
          "tier2_cap_rule" = selected_proposal$tier2_cap_rule,
          "tier3_cap_rule" = selected_proposal$tier3_cap_rule,
          "tier1_cap_value" = selected_proposal$tier1_cap_value,
          "tier1_cap_fishers" = selected_proposal$tier1_cap_fishers,
          "tier1_cap_percent" = selected_proposal$tier1_cap_percent,
          "tier2_cap_value" = selected_proposal$tier2_cap_value,
          "tier2_cap_fishers" = selected_proposal$tier1_cap_fishers,
          "tier2_cap_percent" = selected_proposal$tier2_cap_percent,
          "tier3_cap_value" = selected_proposal$tier3_cap_value,
          "tier3_cap_fishers" = selected_proposal$tier3_cap_fishers,
          "tier3_cap_percent" = selected_proposal$tier3_cap_percent)

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup,
      country_lookup = country_dependencies)

@@

    # Run model
    results <- pmap_df(list(fleet = fleet_list,
                                   region = names(fleet_list),
                                   bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

    # Extract results timeseries
    results_all <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name))

      write_csv(results_all, paste0(results_dir, "results_", str_replace_all(proposal_name, "/", "_"), ".csv"))

@@

>>>>

@@

subsidy_types_sorted_sumaila <- c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types)

# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.75

end_year <- 2080

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

@@

@@

   # Get all Cap/Tier conditions
   cap_tier = 
     list("on_off" = selected_proposal$cap_on_off,
          "subsidy_types" = unlist(str_split(selected_proposal$cap_subsidy_types, ", ")),
          "tier_number" = selected_proposal$cap_tier_number,
          "tier_system" = selected_proposal$tier_system,
          "two_tier_cutoff" = selected_proposal$two_tier_cutoff,
          "three_tier_cutoff" = as.numeric(unlist(str_split(selected_proposal$three_tier_cutoff, ", "))),
          "tier1_cap_rule" = selected_proposal$tier1_cap_rule,
          "tier2_cap_rule" = selected_proposal$tier2_cap_rule,
          "tier3_cap_rule" = selected_proposal$tier3_cap_rule,
          "tier1_cap_value" = selected_proposal$tier1_cap_value,
          "tier1_cap_percent" = selected_proposal$tier1_cap_percent,
          "tier1_cap_best_percent_subs" = selected_proposal$tier1_cap_best_percent_subs,
          "tier1_cap_best_percent_landed_value" = selected_proposal$tier1_cap_best_percent_landed_value,
          "tier1_cap_best_percent_fishers" = selected_proposal$tier1_cap_best_percent_fishers,
          "tier2_cap_value" = selected_proposal$tier2_cap_value,
          "tier2_cap_percent" = selected_proposal$tier2_cap_percent,
          "tier2_cap_best_percent_subs" = selected_proposal$tier2_cap_best_percent_subs,
          "tier2_cap_best_percent_landed_value" = selected_proposal$tier2_cap_best_percent_landed_value,
          "tier2_cap_best_percent_fishers" = selected_proposal$tier2_cap_best_percent_fishers,
          "tier3_cap_value" = selected_proposal$tier3_cap_value,
          "tier3_cap_percent" = selected_proposal$tier3_cap_percent,
          "tier3_cap_best_percent_subs" = selected_proposal$tier3_cap_best_percent_subs,
          "tier3_cap_best_percent_landed_value" = selected_proposal$tier3_cap_best_percent_landed_value,
          "tier3_cap_best_percent_fishers" = selected_proposal$tier3_cap_best_percent_fishers)

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      managed_threshold = managed_cutoff,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      cap_tier_lookup = cap_tier_lookup_table,
      country_lookup = country_dependencies)

@@

    # Run model
    results <- pmap_df(list(fleet = fleet_list,
                                   region = names(fleet_list),
                                   bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = end_year,
                                  return = "all")

    # Extract results timeseries
    results_all <- results %>%
      dplyr::filter(Year > 2018) %>%
      group_by(Year, Variable, Fleet) %>%
      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
      TRUE ~ 0)) %>%
      ungroup() %>%
      mutate(run_id = proposal_name,
             run_name = names(proposal_name),
             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))

      write_csv(results_all, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))

@@

Make plots with all proposals and the most ambitious result

```{r}
# Load most ambitous results from previous script
most_ambitious_results <- read_csv(paste0(here::here("results", "06-run-model/"), "mgmt_threshold_", managed_cutoff, "/", "BC_rel_ts_data.csv")) %>%
  mutate(run_id = "Ambitious Reform",
         run_group = "Ambitious Reform")

plot_results <- proposal_results %>%
  dplyr::filter(run_id != "RD/TN/RL/103") %>%
  bind_rows(most_ambitious_results)

# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                           spatial_res = "global",
                                           temporal_res = "all",
                                           start_year = 2018,
                                           end_year = end_year,
                                           plot_name = "all_proposals_ts_plot",
                                           plot_width = 8,
                                           plot_height = 10,
                                           results_dir = results_dir,
                                           group_var = "run_id",
                                           color_var = "run_group",
                                           legend_pos_manual = "bottom",
                                           legend_name = "Scenario Type")

  # 2) global (aggregated) "kobe" final year plot
  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                            spatial_res = "global",
                                            temporal_res = "last",
                                            end_year = end_year,
                                            plot_name = "all_proposals_end_plot",
                                            plot_width = 8,
                                            plot_height = 8,
                                            results_dir = results_dir,
                                            group_var = "run_id",
                                            color_var = "run_group",
                                            legend_pos_manual = "bottom",
                                            legend_name = "Scenario Type")

  # 3) regional timeseries plot
  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
                                                    spatial_res = "regional",
                                                    temporal_res = "all",
                                                    start_year = 2018,
                                                    end_year = end_year,
                                                    plot_name = "regional_all_proposals_ts_plot",
                                                    plot_width = 12,
                                                    plot_height = 10,
                                                    results_dir = results_dir,
                                                    group_var = "run_id",
                                                    color_var = "run_group",
                                                    legend_pos_manual = "bottom",
                                                    legend_name = "Scenario Type")

  # 4) regional "kobe" final year plot
  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
                                                     spatial_res = "regional",
                                                     temporal_res = "last",
                                                     end_year = end_year,
                                                     plot_name = "regional_all_proposals_end_plot",
                                                     plot_width = 12,
                                                     plot_height = 8,
                                                     results_dir = results_dir,
                                                     group_var = "run_id",
                                                     color_var = "run_group",
                                                     legend_pos_manual = "bottom",
                                                     legend_name = "Scenario Type")
}
```

Make nice looking table showing most ambitious result values (global and regional)

```{r}
# most_ambitious_results_global <- most_ambitious_results %>%
#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
#     summarize(BAU_tot = sum(BAU, na.rm = T),
#               Reform_tot = sum(Reform, na.rm = T),
#               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
#                             TRUE ~ 0)) %>%
#     ungroup() %>%
#     mutate(Region = "Global") %>%
#     # mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
#     #                             Variable == "catches_total" ~ "Catches",
#     #                             Variable == "revenue_total" ~ "Revenue",
#     #                             Variable )) %>%
#   dplyr::filter(Fleet == "Total") %>%
#   dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
```
